\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}

### 2014-01-27 papers/jss/article.Rnw
add nlme citation as we have to cite software anyway
git-svn-id: svn://svn.r-forge.r-project.org/svnroot/rprotobuf@856 edb9625f-4e0d-4859-8d74-9fd3b1da38cb

%
% Local helpers to make this more compatible with R Journal style.
%
\newcommand{\CRANpkg}[1]{\pkg{#1}}
\RequirePackage{fancyvrb}
\RequirePackage{alltt}
\DefineVerbatimEnvironment{example}{Verbatim}{}
% Articles with many authors we should shorten to FirstAuthor, et al.
\shortcites{sciencecloud,janus,dremel}
\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Google, Inc \And
        Jeroen Ooms\\UCLA}
\title{\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}}

@@

\Sexpr{m} data sets can be converted to Protocol Buffers
without loss of information (\Sexpr{format(100*m/n,digits=1)}\%). Upon closer
inspection, all other data sets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes (such as a \emph{formula} object) used by the \pkg{nlme} package.
Because formulas are \proglang{R} \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize\_pb} is used on objects of this class, it will serialize
the data frame and all attributes, except for the formula.

>>>>

%
% Local helpers to make this more compatible with R Journal style.
%
\newcommand{\CRANpkg}[1]{\pkg{#1}}
\RequirePackage{fancyvrb}
\RequirePackage{alltt}
\DefineVerbatimEnvironment{example}{Verbatim}{}
% Articles with many authors we should shorten to FirstAuthor, et al.
\shortcites{sciencecloud,janus,dremel,nlme}
\author{Dirk Eddelbuettel\\Debian Project \And 
        Murray Stokely\\Google, Inc \And
        Jeroen Ooms\\UCLA}
\title{\pkg{RProtoBuf}: Efficient Cross-Language Data Serialization in \proglang{R}}

@@

\Sexpr{m} data sets can be converted to Protocol Buffers
without loss of information (\Sexpr{format(100*m/n,digits=1)}\%). Upon closer
inspection, all other data sets are objects of class \texttt{nfnGroupedData}.
This class represents a special type of data frame that has some additional 
attributes (such as a \emph{formula} object) used by the \pkg{nlme} package \citep{nlme}.
Because formulas are \proglang{R} \emph{language} objects, they have little meaning to
other systems, and are not supported by the \texttt{rexp.proto} descriptor.
When \texttt{serialize\_pb} is used on objects of this class, it will serialize
the data frame and all attributes, except for the formula.
